\documentclass[pdftex,12pt,a4paper]{article}

% just for this template
\usepackage{lipsum}

% For graphics
\usepackage[pdftex]{graphicx}
% you can place a figure at the position where it occurs in the text using [H]
\usepackage{here}

% For flexible tables
\usepackage{multirow}

% In case you need umlauts
% \usepackage[utf8]{inputenc}


% Sophisticated citation.
% Check out: http://merkel.zoneo.net/Latex/natbib.php
\usepackage{natbib}

% Math symbols not defined in the usual package, e.g. arrows that are crossed.
\usepackage{amssymb}

% Arrows with text / superscript
\usepackage{amsmath}
\usepackage{tipa}
% Different font - something like Arial
%\usepackage{mathptmx}

% Adjust margin of paper.
\usepackage{geometry}
\geometry{a4paper, top=25mm, left=25mm, right=25mm, bottom=25mm}

% Zeilenabstand 1.25 %
\linespread{1.2}

% Example Environments
\usepackage{amsthm}
\newtheoremstyle{style}   
  {0.5cm}              %Space above    
  {-0.8cm}              %Space below
  {}                      %Body font: original {\normalfont}    
  {}                      %Indent amount (empty = no indent,%\parindent = paraindent)    
  {\normalfont\bfseries}  %Thm head font original       
  {{\normalfont\bfseries \thmname{#1}\thmnumber{ #2}}}
\theoremstyle{style}
\newtheorem{example}{Example}[section]

% Formula Environments
\newtheorem{formula}{Formula}[section]

% Computational Linguistics trees etc.
\usepackage{xyling}

% Nicer captions
\usepackage{caption2}
\newcaptionstyle{mystyle}{%
  \normalcaptionparams
  \renewcommand\captionlabelfont{\bfseries}%
  \renewcommand\captionlabeldelim{.}%
  \onelinecaptionsfalse
  \usecaptionstyle{centerlast}}

\captionstyle{mystyle}

% Table of contents depth
\setcounter{tocdepth}{3}

% A horizontal rule for the title page
\newcommand{\HRule}{\rule{\linewidth}{0.5mm}}

% Paragraph and indent (as required by Prof. Dr. Pinkal)
\setlength{\parindent}{0pt}
\setlength{\parskip}{2ex plus 0.5ex minus 0.2ex}

\begin{document}

% Include the title page (modify title.tex!)
\input{title.tex}

\setcounter{page}{1}		% Seitenzähler auf 1 setzen %
%\pagestyle{fancy}				% fancy header style
\pagenumbering{arabic}
%\thispagestyle{empty}
\begin{abstract}
\setlength{\parskip}{2ex plus 0.5ex minus 0.2ex}

% Please put \noindent before each paragraph of the abstract!
\noindent Second language (L2) learners often struggle with correctly perceiving and producing vowels in their target language.  These errors are believed to be caused by interference from the native language phonology of the learners \citep{flege1995second, and more}, which prevents them from correctly forming new phonological categories for one or more of the vowel in the target language. In the case of L2 German learners, this is a phenomenon of particular concern due to the relatively large German vowel inventory, which includes many vowel categories which are separated by very slight changes in spectral and/or durational information. \citep{patzold1997acoustic} This dense vowel space presents a challenge for learners with a much sparser L1 vowel system, as they must attempt to form many new vowel categories in regions of the vowel space where new vowels could easily be misperceived or assimilated to existing L1 categories \citep{}. In order to assist L2 German learners in the correct formation of new vowel categories, a Computer Assisted Pronunciation Training (CAPT) tool is proposed to providing visual feedback describing the most important differences between German vowels. The research, development, and testing of this Pronunciation Training tool is thus proposed as the topic of this masters thesis. 

\noindent  The preparatory stage of the Thesis will consist of a survey of relevant literature in order to provides sound theoretical motivation for the functionality and design of the CAPT tool. The next stage of the thesis will be development of the tool itself, which will build upon a proof of concept system by Carroll, Trouvain and Zimmerer \citep{}. Improvements to the proof of concept system to be performed during the thesis include: tracking users progress, vowel recognition with forced alignment, and a system to customize vowel category targets based on the individual use vowel space. The user interface will also undergo improvements to be more visually intuitive, and to include supplementary information about tongue and jaw position. The third stage of the thesis will be focused on testing the effectiveness CAPT system. Therefore, an experiment will be designed to determine if the CAPT system performs better than control groups receiving no language instruction, or standard classroom language instruction.  If sufficient subjects can be obtained for a live trial, the experiment will then be carried out.

\end{abstract}
\newpage

% Table of contents
%\thispagestyle{empty}
%\tableofcontents
%\newpage

% Start of content

\newpage
\input{literatureSearch}

\input{SystemDevelopment}

\input{Testing}

\input{Conclusion}

% REFERENCES
\newpage
\bibliographystyle{apalike}
\bibliography{references}

\end{document}
